---
title : "STA 141A Project"
author : "Jay Bendre, John Dinh, Grant Gambetta and Ignat Kulinka"
output: 'html_document'
--- 

----
<Add Changes above this please>
----

# Final Implementation of the Project

## Exploratory Data Analaysis

```{r message = FALSE,warning = FALSE}
# Importing all the required libraries
library(tidyverse)
library(ggplot2)
library(plotly)
library(ipumsr)
library(haven)
library(splitstackshape)
library(caret)
library(randomForest)
library(extrafont)
library(ggpubr)
library(stargazer)
library(randomForestExplainer)
library(extrafont)
library(ggpubr)
library(MASS)

# fix for dplyr select
select <- dplyr::select 

```

```{r}
# A. Loading the data and creating a dataframe
df_ddi <- read_ipums_ddi("Dataset/nhis_00001.xml")
df <- as.data.frame(read_ipums_micro(df_ddi, verbose = FALSE))
# df %>% head(5)
```

```{r}
# B. Preliminary check on the data
#  1. Rows/cols
# c(nrow(df), ncol(df))

#  2. Review classes
# sapply(df, class)
# Note: some of the variables have attached data definitions "haven labeled"

# C. Check for missing values
# sapply(df, function(x) sum(is.na(x)))

# D. Dropping variables that are not that important or provide no inisghts in the data
droppable_cols <- c("YEAR","SERIAL","STRATA","PSU","NHISPID","HHX","SAMPWEIGHT","LONGWEIGHT","PARTWEIGHT", "PERNUM")
df <- df %>% select(-all_of(droppable_cols))
# colnames(df)

# E. Function to plot variables
#  1. Make a function to plot a single distribution
plot_var <- function(col, title){
	plt_dt <- df %>% mutate(var_factor2 := as_factor({{col}})) %>% 
		group_by(var_factor2) %>% 
		summarize(cnt = n()) %>% 
		mutate(prc = cnt/sum(cnt))
	
	p <- ggplot(plt_dt, aes(x=reorder(var_factor2, cnt, sum), y=cnt)) +
		geom_col(fill = "steelblue", color = "black", width = .5) +
		scale_y_continuous(name = "Count of Respondents", labels = scales::comma_format(), expand = expansion(mult = c(0, .3))) +
		scale_x_discrete(name = "", labels = function(x) str_wrap(x, width = 15)) +
		labs(title = paste0(title)) +
		coord_flip() +
		geom_text(label = scales::percent(plt_dt$prc, accuracy = 0.1), hjust = -0.15) + 
		theme_classic() +
		theme(plot.title = element_text(size = 16, hjust = 0.5),
								axis.text = element_text(size = 13),
								axis.title = element_text(size = 14),
								aspect.ratio = 1/2,
								text = element_text(family = "Times New Roman"))
	
	return(p)
}

#  2. Plot COVID-related response variables as an example
covid_vars_plt <- ggarrange(plot_var(CVDDIAG, "Ever Told had or\nLikely had Coronavirus"),
																	plot_var(CVDTEST, "Ever Been Tested\n for Coronavirus"),
																	ncol=2, align = "hv") 

# F. Summarize data variables
#  1. Quick info on the variables
smry <- data.frame(var_name = names(df),
																			# initial_data_type = sapply(df, function(x) class(x)[3]),
																			desc = sapply(df, function(x) attributes(x)$label),
																			final_data_type = ifelse(sapply(df, function(x) class(x)[3]) == "integer", "factor", "numeric"),
																			num_niu = sapply(df, function(x) sum(as_factor(x)=="NIU")), row.names = NULL)

#  2. Stargazer for the report
# stargazer(smry, summary = FALSE)

```


```{r}
# G. Handling SEX AND SEXORIEN variable
#  1. Combining all 'unknown categories' into one
unk <- c(7,8,9)
df$SEX[df$SEX %in% unk] <- 9

#  2. Combining Unknown SEXORIEN into "Something else" category
unk <- c(5,7,8)
df$SEXORIEN[df$SEXORIEN %in% unk] <- 4

# H. Handling RACEA Variable
#  1. Combining all 'unknown categories' into one
unk <- c(580, 900, 970, 980, 990)
df$RACEA[df$RACEA %in% unk] <- 900

# I. Handling MARSTAT & MARST Variable
#  1. Review/compare distributions
# df %>%
# 	group_by(MARSTAT=as_factor(MARSTAT), MARST=as_factor(MARST)) %>%
# 	summarise(n())

#  2. Keep current marital status for this analysis since both are similar
df <- df %>%
	select(-MARSTAT)

#  3. Combine NIU and Unknown into one 
unk <- c(0,99)
df$MARST[df$MARST %in% unk] <- 99

#  4. Combine all married labels into one
marr <- c(10,11,12,13)
df$MARST[df$MARST %in% marr] <- 10

# J. Handling FAMSIZE 
#  1. Combine Unknowns into one
unk <- c(98,99)
df$FAMSIZE[df$FAMSIZE %in% unk] <- 98

# K. Handling PARTNEREMP
#  1. Combine various levels of unknown response
unk <- c(7,8,9)
df$PARTNEREMP[df$PARTNEREMP %in% unk] <- 9

# L. Handling ARMFEV
#  1. Combine all levels of unknown
unk <- c(97,98,99)
df$ARMFEV[df$ARMFEV %in% unk] <-  99

# M. Handling EDUC, SPOUSEDUC, SCHOOLNOW, by combining all unknowns
unk <- c(996,997,998,999)
df$EDUC[df$EDUC %in% unk] <- 996

unk <- c(97,98,99)
df$SPOUSEDUC[df$SPOUSEDUC %in% unk] <- 99

unk <- c(7,8,9)
df$SCHOOLNOW[df$SCHOOLNOW %in% unk] <- 9

# N. Handling Employment Status  
#  1. Working responses
work <- c(110,111,112)
df$EMPSTAT[df$EMPSTAT %in% work] <- 110

#  2. With job
w_job <- c(120,121,122)
df$EMPSTAT[df$EMPSTAT %in% w_job] <- 120

#  3. Unemployed
unemployed <- c(200,210,211:217)
df$EMPSTAT[df$EMPSTAT %in% unemployed] <- 200

#  4. Unknown
unk <- c(997:999)
df$EMPSTAT[df$EMPSTAT %in% unk] <- 999

# O. Handling HOURSWRK by replacing number of hours unknown into 0
unk <- c(0,97:99)
df$HOURSWRK[df$HOURSWRK %in% unk] <- 0

# P. Handling PAIDSICK
#  1. Combined unknowns into one
df <- df %>%
	mutate(PAIDSICK = replace(PAIDSICK, PAIDSICK > 4, 9))  

# Q. Mutating EMPHI and EMPFT
df <- df %>% 
	mutate(EMPHI = replace(EMPHI, EMPHI > 4, 9))  

df <- df %>% 
	mutate(EMPFT = replace(EMPFT, EMPFT > 7, 7))  

# R. Mutating USUALPL
df <- df %>% 
	mutate(USUALPL = replace(USUALPL, USUALPL == 3,2))  

df <- df %>% 
	mutate(USUALPL = replace(USUALPL, USUALPL >= 7,9))  

# S. Mutating HINOTCOVE
#  1. Combine all unknowns into one
df <- df %>% 
	mutate(HINOTCOVE = replace(HINOTCOVE,HINOTCOVE >4,9))  

# T. Mutating CVDTEST
#  1. Combine all unknowns into one
df <- df %>% 
	mutate(CVDTEST = replace(CVDTEST,CVDTEST >4,9))  

# U. Mutating CVDDIAG
#  1. Combine all unknowns into one
df <- df %>%
	mutate(CVDDIAG = replace(CVDDIAG,CVDDIAG >4,9))  

# V. Mutating CVDTESTRSLTS
#  1. Combine all unknowns into one
df <- df %>% 
	mutate(CVDTESTRSLT = replace(CVDTESTRSLT,CVDTESTRSLT >4,9))  
```

## Data Visualization on the clean data

```{r message=FALSE, warning=FALSE}
# W. Review relation ship between health insurance coverage and coronavirus infection 
#  1. Summarize data and filter to complete data
plt_dt <- df %>% 
	mutate(HINOTCOVE=as_factor(HINOTCOVE),
								CVDTESTRSLT=as_factor(CVDTESTRSLT)) %>% 
	filter(HINOTCOVE %in% c("Yes, has no coverage",
																									"No, has coverage") &
								CVDTESTRSLT %in% c("Yes", "No")) %>% 
	group_by(HINOTCOVE, CVDTESTRSLT) %>% 
	summarize(cnt = n()) %>% 
	ungroup() %>% 
	group_by(HINOTCOVE) %>% 
	mutate(prcnt = cnt/sum(cnt)) %>% 
	arrange(HINOTCOVE)

#   HINOTCOVE            CVDTESTRSLT   cnt  prcnt (total)
# 1 No, has coverage     No           4659 0.860 
# 2 No, has coverage     Yes           440 0.0812
# 3 Yes, has no coverage No            259 0.0478
# 4 Yes, has no coverage Yes            59 0.0109

#  2. Plot stacked barchart for all four groups 
ggplot(plt_dt, aes(x=CVDTESTRSLT, y=cnt, fill=CVDTESTRSLT)) +
	geom_bar(position = "dodge", stat="identity", color="black") +
	facet_wrap(~HINOTCOVE,
												labeller = labeller(HINOTCOVE = c("No, has coverage" = "Health Insurance Coverage",
																																														"Yes, has no coverage" = "No Health Insurance Coverage"))) +
	scale_x_discrete("Had Coronavirus According to Test", labels=c("Negative", "Positive")) +
	scale_y_continuous(name = "Count of Respondents", 
																				labels = scales::comma_format(), expand = expansion(mult = c(0, .2))) +
	scale_fill_manual(values=c("#4682B4", "#B47846")) +
	geom_text(label = scales::percent(plt_dt$prcnt, accuracy = 0.1), 
											position = position_dodge(width=0.9), vjust=-0.5) +
	theme_classic() +
	theme(legend.position="none",
							text = element_text(family = "Times New Roman"),
							aspect.ratio = 1/2,
							axis.text = element_text(size = 13),
							axis.title = element_text(size = 14),
							strip.text = element_text(size = 13))




```


```{r}
# X. Seeing results between getting sick leave and covid result tests
#  1. Summarize and filter data
plt_dt2 <- df %>% 
	group_by(PAIDSICK = as_factor(PAIDSICK), CVDTESTRSLT = as_factor(CVDTESTRSLT)) %>%
	summarize(count = n()) %>% 
	filter(PAIDSICK %in% c("Yes", "No") &
								CVDTESTRSLT %in% c("Yes", "No")) %>% 
	group_by(PAIDSICK) %>% 
	mutate(prcnt = count/sum(count)) %>% 
	arrange(PAIDSICK)

ggplot(plt_dt2, aes(fill=CVDTESTRSLT, y=count, x=CVDTESTRSLT)) + 
	geom_bar(position="dodge", stat="identity", color = "black") +
	facet_wrap(~PAIDSICK, labeller = labeller(PAIDSICK = c("No" = "No Paid Sick Leave at Current Job", "Yes" =  "Paid Sick Leave at Current Job"))) +
	scale_y_continuous(name = "Count of Respondents", labels = scales::comma_format(), expand = expansion(mult = c(0, .2))) +
	geom_text(label = scales::percent(plt_dt2$prcnt, accuracy = 0.1), position = position_dodge(width=0.9), vjust=-0.25) +
	xlab("Had Coronavirus According to Test") + 
	scale_x_discrete(labels = c("No","Yes")) + 
	scale_fill_manual(values = c("#4682B4","#B47846")) + 
	theme_classic() + 
	theme(legend.position="none",
							text = element_text(family = "Times New Roman"),
							aspect.ratio = 1/2,
							axis.text = element_text(size = 13),
							axis.title = element_text(size = 14),
							strip.text = element_text(size = 13))

```

```{r fig, fig.width= 8, fig.height = 8}
# Y. Seeing the number of people who got tested given they have health insurance coverage from the company
sample_df <- df %>% 
	group_by(CVDTEST = as.factor(CVDTEST), EMPHI = as.factor(EMPHI)) %>%
	summarize(count = n()) %>% 
	filter(CVDTEST %in% c(1,2) &
								EMPHI %in% c(1, 2)) %>% 
	group_by(EMPHI) %>% 
	mutate(prcnt = count/sum(count)) %>% 
	arrange(EMPHI)

ggplot(sample_df, aes(fill=CVDTEST, y=count, x=CVDTEST)) + 
	geom_bar(position="dodge", stat="identity", color = "black") +
	facet_wrap(~EMPHI, labeller = labeller(EMPHI = c("0" = "NIU","1" =  "Employer Insurance Not Offered", "2" = "Employer Insurance Offered", "9" = "Unknown"))) +
	scale_y_continuous(name = "Count of Respondents", labels = scales::comma_format(), expand = expansion(mult = c(0, .2))) +
	geom_text(label = scales::percent(sample_df$prcnt, accuracy = 0.1), position = position_dodge(width=0.9), vjust=-0.25) +
	xlab("Ever Been Tested for Coronavirus") + 
	scale_x_discrete(labels = c("No","Yes")) + 
	scale_fill_manual(values = c("#4682B4","#B47846")) + 
	theme_classic() + 
	theme(legend.position="none",
							text = element_text(family = "Times New Roman"),
							aspect.ratio = 1/2,
							axis.text = element_text(size = 13),
							axis.title = element_text(size = 14),
							strip.text = element_text(size = 13))
```

```{r}
# Z. Does having a usual place for medical care affect the testing
plt_dt3 <- df %>% 
	group_by(USUALPL = as_factor(USUALPL), CVDTEST = as_factor(CVDTEST)) %>%
	summarize(count = n()) %>% 
	filter(USUALPL %in% c("Yes, has a usual place or Yes", "There is no place or No") &
								CVDTEST %in% c("Yes", "No")) %>% 
	group_by(USUALPL) %>% 
	mutate(prcnt = count/sum(count)) %>% 
	arrange(USUALPL)

ggplot(plt_dt3, aes(x=CVDTEST, y=count, fill=CVDTEST)) + 
	geom_bar(position="dodge", stat="identity", color = "black") +
	facet_wrap(~USUALPL, labeller = labeller(USUALPL = c("There is no place or No" = "No Usual Place Medical Care","Yes, has a usual place or Yes" =  "Has Usual Place for Medical Care"))) +
	scale_y_continuous(name = "Count of Respondents", labels = scales::comma_format(), expand = expansion(mult = c(0, .2))) +
	geom_text(label = scales::percent(plt_dt3$prcnt, accuracy = 0.1), position = position_dodge(width=0.9), vjust=-0.25) +
	xlab("Ever Been Tested for Coronavirus") + 
	scale_x_discrete(labels = c("No","Yes")) + 
	scale_fill_manual(values = c("#4682B4","#B47846")) + 
	theme_classic() + 
	theme(legend.position="none",
							text = element_text(family = "Times New Roman"),
							aspect.ratio = 1/2,
							axis.text = element_text(size = 13),
							axis.title = element_text(size = 14),
							strip.text = element_text(size = 13))
```


## Data Modelling

### Question 1: How does socioeconomic status affect COVID-19 infection status?

```{r}
# AA. Create a stratified sample
#  1. Review CVDDIAG distribution
df %>% 
	group_by(CVDDIAG_CD=CVDDIAG,
										CVDDIAG=as_factor(CVDDIAG)) %>% 
	summarize(Count = n())

#  2. Exclude NIU and Unknown values
sample_df <- df %>%
	filter(!(CVDDIAG %in% c(0,9)))

#  3. Create a stratified sample of the data
set.seed(1234)
strat <- stratified(sample_df,
																				group = 'CVDDIAG',
																				size = 2000)

#  4. Refactor the sample to zero's and one's
strat <- strat %>% 
	mutate(CVDDIAG = as.factor(CVDDIAG-1))

#  5. Review the distribution 
strat %>%
	group_by(CVDDIAG) %>% 
	summarize(Count = n()) %>% 
	mutate(Percent_Total = Count/sum(Count))

#  6. Visualising it
strat_plt <- strat %>%
	group_by(CVDDIAG) %>% 
	summarize(cnt = n()) %>% 
	mutate(prc = cnt/sum(cnt))

ggplot(strat_plt, aes(x=CVDDIAG, y=cnt)) +
	geom_col(color = "black", fill=c("#4682B4","#B47846")) +
	scale_y_continuous(name = "Count of Cases",
																				labels = scales::comma_format(),
																				expand = expansion(mult = c(0, .1))) +
	theme_classic() + 
	geom_text(label = scales::percent(strat_plt$prc, accuracy = 0.1),
											position = position_dodge(width=0.9), vjust=-0.25) +
	scale_x_discrete("Ever Told had or Likely had Coronavirus",
																		labels = c("No","Yes")) + 
	theme(legend.position="none",
							text = element_text(family = "Times New Roman"),
							aspect.ratio = 1/2,
							axis.text = element_text(size = 13),
							axis.title = element_text(size = 14),
							strip.text = element_text(size = 13))

```

```{r}
# AB. Split data into training and testing
set.seed(101)
idx <- sample.int(n = nrow(strat),
																		size = floor(0.70 * nrow(strat)),
																		replace = F)
s.train <- strat[idx,]
s.test <- strat[-idx,]

# AC. Selecting personal information variables
#  1. Create a vector of column names
per_info_vars <- c("AGE", "SEX", "MARST", "RACEA",
																			"SEXORIEN", "EDUC", "ASTATFLG",
																			"CSTATFLG","EDUC","REGION","CVDDIAG")

#  2. Subset training and testing datasets
data_to_study.train <- s.train %>% 
	select(all_of(per_info_vars)) 

data_to_study.test	 <- s.test %>% 
	select(all_of(per_info_vars))
	
#  3. Use stepAIC to find the optimal combination of variables
model <- glm(CVDDIAG ~ ., data_to_study.train, family = 'binomial') %>%
	stepAIC(trace = FALSE, k=2)

#  4. Review model summary
summary(model)

#  5. Review the confusion matrix 
lr_probs <- predict(model, newdata = data_to_study.test, type = 'response')
lr_predicted <- ifelse(lr_probs < 0.5, 0, 1)
confusionMatrix(factor(lr_predicted),
																factor(data_to_study.test$CVDDIAG))
```


```{r}
library(stargazer)
conf.mat <- as.data.frame.matrix(cf$table)
stargazer(conf.mat, title = "Confusion Matrix", summary = FALSE)
```

### Question 2
What are the driving factors behind infections? 

```{r}
# A. Using logistic regression to see what affects the diagnosis and selecting the best model using stepAIC

library(randomForestExplainer)

# Creating samples

x.train <- s.train %>% dplyr::select(-CVDDIAG)
y.train <- s.train %>% dplyr::select(CVDDIAG)

x.test <- s.test %>% dplyr::select(-CVDDIAG)
y.test <- s.test %>% dplyr::select(CVDDIAG)

model.rf <- randomForest::randomForest(x = x.train, y = as.factor(y.train$CVDDIAG), ntree = 500, importance = T, proximity = T)
print(model.rf)
print(importance(model.rf,2))

plot(model.rf)

predictions <- predict(model.rf, newdata = x.test)
cf.rf <- confusionMatrix(predictions,droplevels(as.factor(y.test$CVDDIAG)))


frame <- measure_importance(model.rf)
frame
plot_importance_ggpairs(frame)

```

```{r}
plot_importance_rankings(frame)
```

```{r}

imp <- as.data.frame(model.rf$importance[,3:4])

imp <- imp %>% arrange(desc(MeanDecreaseGini))

ggplot(imp, aes(x = reorder(rownames(imp), MeanDecreaseGini), y = MeanDecreaseGini, fill = rownames(imp))) + geom_bar(stat = "identity") + ggtitle("Variable Importance based on MeanDecreaseGini") + theme_minimal() + coord_flip() + xlab("Variables") + ylab("Importance of the variables")
```

### Question 3
What type of working conditions impacts the ability to get tested for COVID? 

```{r}
df_ddi <- read_ipums_ddi("Dataset/nhis_00001.xml")
df <- as.data.frame(read_ipums_micro(df_ddi, verbose = FALSE))
cvd_test_df <- df %>% dplyr::filter(CVDTEST == 1 | CVDTEST == 2) # select only yes or no for covid test variable
cvd_test_df$CVDTEST  <- ifelse(cvd_test_df$CVDTEST == 1, 0, 1) # relevel covid test variable: # 0 = no test, 1 = test
barplot(table(cvd_test_df$CVDTEST))
cvd_test_df <- cvd_test_df %>% dplyr::select(NHISHID, SEX, AGE, FAMSIZE, EMPSTAT, HOURSWRK, PAIDSICK, EMPHI, EMPFT, USUALPL, HINOTCOVE, INCFAM07ON, FAMTOTINC, CVDTEST)
# re factor variables, 7 = unknown
cvd_test_df$PAIDSICK[cvd_test_df$PAIDSICK == 8] = 7
cvd_test_df$PAIDSICK[cvd_test_df$PAIDSICK == 9] = 7
cvd_test_df$EMPHI[cvd_test_df$EMPHI == 8] = 7
cvd_test_df$EMPHI[cvd_test_df$EMPHI == 9] = 7
cvd_test_df$EMPFT[cvd_test_df$EMPFT == 8] = 7
cvd_test_df$EMPFT[cvd_test_df$EMPFT == 9] = 7
cvd_test_df$USUALPL[cvd_test_df$USUALPL == 8] = 7
cvd_test_df$USUALPL[cvd_test_df$USUALPL == 9] = 7
cvd_test_df$HOURSWRK <- as.double(cvd_test_df$HOURSWRK)
cvd_test_df <- cvd_test_df %>% mutate_if(is.integer, as.factor)
cvd_test_df
# oversample the data
set.seed(123)
vec <- c(3000, 2000)
names(vec) <- c(0, 1)
strat_sample <- stratified(cvd_test_df, group = 'CVDTEST', size = vec)
strat_sample

table(strat_sample$CVDTEST)/length(strat_sample$CVDTEST)
barplot(table(strat_sample$CVDTEST))
set.seed(123)
lr_train <- strat_sample %>% dplyr::sample_frac(0.70)
lr_test <- dplyr::anti_join(strat_sample, lr_train, by = "NHISHID")
lr_train <- lr_train %>% dplyr::select(-c("NHISHID"))
lr_test <- lr_test %>% dplyr::select(-c("NHISHID"))

lr2 <- glm(data = lr_train, CVDTEST ~ ., family = 'binomial')
summary(lr2)
null_model <- glm(data = lr_train, CVDTEST ~ 1, family = 'binomial')
full_model <- glm(data = lr_train, CVDTEST ~ ., family = 'binomial')
step <- stepAIC(null_model, scope = list(lower = ~1, upper = full_model), direction = 'both', k = 2, trace = 0)
step$anova
# final model
lr2 <- glm(data = lr_train, CVDTEST ~ EMPSTAT + HINOTCOVE + AGE + USUALPL + FAMTOTINC, family = 'binomial')
summary(lr2)
lr2_probs <- predict(lr2, newdata = lr_test, type = 'response')
lr2_predicted <- ifelse(lr2_probs < 0.5, 0, 1)

confusionMatrix(factor(lr2_predicted, levels=min(lr_test$CVDTEST):max(lr_test$CVDTEST)), factor(lr_test$CVDTEST, levels=min(lr_test$CVDTEST):max(lr_test$CVDTEST)))
```

### Function
Emprically estimate the distributions of the predictors

Inputs: 
a. Number of replicates
b. Model spec
c. Data

Output:
a. Table to compare classical to emprirical confidence interval
b. Histogram plot of the emperical distribution



```{r}
# A. 
require(boot)
require(kable)
require(reshape2)

# A. Write boot.fn()
cust.boot.fn <- function(x, indices){
	x <- x[indices, ]
	# fit logistic regression
	m_log_tmp <- glm(CVDTEST ~ EMPSTAT + HINOTCOVE + AGE + USUALPL + FAMTOTINC, data = x, family = binomial)
	
	# obtain and return the estimates
	return(summary(m_log_tmp)$coefficients[, c(1)])
}

# B. Run boot
run_boot <- function(dt, repl_num, seed){
	
	# 1. Set seed and run boot
	set.seed(as.numeric(seed))
 boot_est <- boot(data = dt, statistic = cust.boot.fn, R = repl_num)

 # 2. Fit model on all data
 m_log <- glm("CVDTEST ~ EMPSTAT + HINOTCOVE + AGE + USUALPL + FAMTOTINC",
 													data = dt, family = binomial)
 
 # 3. Create summary comparison
 tbl_out <- data.frame(og_est = summary(m_log)$coefficients[, c(2)],
																						boot_est = apply(boot_est$t,2,sd)) %>%	
 	mutate(diff = og_est - boot_est) %>% 
 	kable(col.names = c("Original Model", "Boostrap", "Difference"), digits = 2)
 
 # 4. Plot
 p <- ggplot(melt(data.frame(boot_est$t)) %>%
 								mutate(variable=as.numeric(str_remove(variable, "X"))-1), aes(x=value)) + 
	geom_histogram(bins = 30) + 
	facet_wrap(variable~., scales = "free_x", labeller = label_bquote(beta [.(variable)])) +
	theme_classic2() +
	ylab("Frequency")+
	xlab("Value")
 
 # 5. Return results
 return(list(tbl_out, p, boot.ci(boot_est)))
}

run_boot(dt = lr_train,
									repl_num = 100,
									seed = 123)

```


## Generating LATEX
```{r results = 'asis'}
library(stargazer)
model <-  glm(data = data_to_study.train, CVDDIAG ~ ., family = 'binomial') %>% stepAIC(trace = FALSE, k=2)

stargazer(model,lr2, align = TRUE, type = "html")
```

```{r}
stargazer(cf)
```